International Relations are a Social Network:\\ A Latent Network Approach for Global Politics

### 2017-10-20 paper/4_app.tex
getting there

\begin{figure}
\includegraphics[width=\textwidth]{ABplot_rose_top10.pdf}
 \caption{Nodal Random Effects for AME estimation of Rose (2004).}\label{fig:roser}
\end{figure}

@@

% sd.rowmean sd.colmean   dyad.dep  triad.dep 
% 0.03210221 0.03210221 0.99362646 0.00130249

NEW GRAPHICS TO COME AND BE DESCRIBED.

\begin{figure}
\caption{\label{fig:gibler:dyadtriad} The left panel is  a plot of the dyadic dependencies in the Gibler model 6; the right panel shows the triad dependencies.  Note that the red line represents the null hypothesis of no dependencies, indicating that the standard logistic approach is far from what is uncovered with this analysis. }
\includegraphics[width=\textwidth]{netplots}
\end{figure}
\FloatBarrier

>>>>

\begin{figure}
\includegraphics[width=\textwidth]{rose_aeff_top10.pdf}
 \caption{Nodal Random Effects for AME estimation of Rose (2004).}\label{fig:roser}
\end{figure}

@@

% % SM to MW: hmmm we should talk about the utility of this.
% see fig gibler_srmvc.pdf in the paper dir
% \begin{figure}
% 	\caption{}
% 	\includegraphics[width=\textwidth]{gibler_srmvc.pdf}
% 	\label{fig:gibler:dyadtriad}
% \end{figure}
% \FloatBarrier
